---
title: "my digital shadow"
author: "Hang Yin"
date: "2/14/2021"
output: 
  html_document:
    keep_md: yes
    code_folding: hide
---

```{r, warning=FALSE, results='hide'}
library(dplyr)
library(jsonlite)
library(lubridate)
library(gghighlight)
library(spotifyr)
library(tidyverse)
library(knitr)
library(ggplot2)
library(plotly)
library(fmsb)
library(factoextra)
library(RColorBrewer)
library("GISTools")

library(tm)
library(SnowballC)
library("wordcloud")
library(readr)
library(dplyr)
library(e1071)
library(mlbench)
library(makeFlow)

# Connecting spotify API
client_id <- "9161e59c250e4e5eb9704349f3ae353b"
sec_id <- "55cfbe3dcc8f40739bb622a8e3a015f0"
Sys.setenv(SPOTIFY_CLIENT_ID = '9161e59c250e4e5eb9704349f3ae353b')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '55cfbe3dcc8f40739bb622a8e3a015f0')
get_spotify_authorization_code()
spotifyr::get_spotify_access_token()
token <- "BQBEayfPdUYTSGwPacT9lYJHOe-KtbhVKux7OiBUnrZBJB3pclAfvgasi-VsAoI2bQZnZ2rsFs7ejT-2m4I"

```


## Personal Listening History
```{r}
## total played time(hour) and total artist 
stream_df <- fromJSON("MyData/StreamingHistory0.json", flatten = TRUE)
total_time <- sum(stream_df$msPlayed)/1000/3600 
#366h
total_artist <- length(unique(stream_df$artistName)) 
#724
total_track <- length(stream_df$trackName)  
#8689
unique_track <- length(unique(stream_df$trackName)) 
#2086
track_repeat <- table(stream_df$trackName)
head(sort(table(stream_df$trackName), decreasing = T), n = 10)
```

```{r}
stream_df <-  stream_df %>% 
  filter(endTime < "2021-01-01") %>% 
  mutate(date_time = ymd_hm(endTime, tz = NULL), endTime = NULL) 

stream_df$weekdays <- weekdays(stream_df$date_time)

stream_df <-  stream_df %>%
  mutate(months = month.abb[month(stream_df$date_time)])

breaks <- hour(hm("00:00", "6:00", "12:00", "18:00", "23:59"))
labels <- c("Midnight", "Morning", "Afternoon", "Evening")
stream_df$time_of_day <- cut(x=hour(stream_df$date_time), breaks = breaks, labels = labels, include.lowest=TRUE)

month_max <-stream_df %>%
  group_by(months) %>%
  count(trackName) %>% 
  top_n(1) %>% 
  distinct(months,.keep_all = TRUE) %>%
  arrange(match(months, month.abb))

month_time <- stream_df %>%
  group_by(months, time_of_day) %>%
  summarise(time_h = sum(msPlayed)/1000/60/60)

weekdays_play <- stream_df %>% 
  group_by(weekdays) %>%
  summarize(hours = sum(msPlayed) / 3600000) %>% 
  arrange(weekdays)
stream_df$quarter <- quarter(stream_df$date_time)
weekdays_play <- stream_df %>% 
  group_by(weekdays, quarter) %>%
  summarize(hours = sum(msPlayed) / 3600000) 
view(weekdays_play)

weekdays_play$weekdays <- factor(weekdays_play$weekdays, levels= c("Sunday", "Monday", 
                                         "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
weekdays_play <- weekdays_play[order(weekdays_play$weekdays),]



  
```

## Plots

```{r, echo=FALSE}
ggplot(month_max, aes(ordered(month_max$months, month.abb), 
                      month_max$n,label = month_max$trackName)) + 
  geom_segment(aes(x = ordered(month_max$months, month.abb), xend = ordered(month_max$months, month.abb),  y= 0, yend = month_max$n), color = "grey") +
  geom_point(stat = "identity",colour = "dark green", fill = "dark green") +
  ylim(0,60) +
  coord_flip() +
  geom_text(size = 3.5,hjust = -0.1) + 
  labs(x= "Month", y= "most played song of the month") +
  theme_classic()
# title = "My Monthly Top Songs"

ggplot(month_time, aes(ordered(month_time$months,month.abb), month_time$time_h)) + 
  geom_col(aes(fill = time_of_day)) +
  scale_fill_brewer(palette="Greens") + 
  labs(x= "Months", y= "Hours of Music", fill = "Time of the Day") +
  theme_classic()
#title = "How much time did I spend on Spotify"
 
ggplot(weekdays_play, aes(x = weekdays,y = hours/13, group = factor(quarter),colour = factor(quarter))) + 
    geom_line(size = 1) + geom_point (stat = "identity", size = 2)+
  scale_color_brewer(palette ="Paired") +
labs(x= "Date", y= "Hours of music", colour = "Quarter")  + theme_classic()
     #title = "My Listening pattern Throughout the Week")
```

##  Spotify API
```{r}
# getting my top genre
 artist_genre <-  get_my_top_artists_or_tracks(type = 'artists', time_range = 'long_term', limit = 50) 
 artist_genre <- artist_genre %>%
    rowwise %>% 
    mutate(genres = paste(genres, collapse = ', ')) 
```

```{r}
# create texting plot 
corpus = Corpus(VectorSource(artist_genre$genres))

#Removing Punctuation
corpus = tm_map(corpus, removePunctuation)

for (i in c(1:50)) {
  print(corpus[[i]][1])
}

# create frequency matrix
DTM <- TermDocumentMatrix(corpus)
text_matrix <- as.matrix(DTM)
f <- sort(rowSums(text_matrix),decreasing=TRUE)
text_df <- data.frame(word = names(f),freq=f)
text_df
```


```{r}
# Text graph
set.seed(124)
wordcloud(words = text_df$word, freq = text_df$freq, min.freq = 1, random.order=FALSE, rot.per=0.5, colors= brewer.pal(12,"Dark2"))
```


## 12 months/6 months/3 months prefer audio features
```{r}
# getting tracks id
year_fav <- get_my_top_artists_or_tracks(type = "tracks", limit = 50, offset = 0,
 time_range = "long_term",authorization = get_spotify_authorization_code(),include_meta_info = FALSE)
 
half_year_fav <- get_my_top_artists_or_tracks(type = "tracks", limit = 25, offset = 0,
time_range = "medium_term", authorization = get_spotify_authorization_code(),
 include_meta_info = FALSE)

recent_fav <- get_my_top_artists_or_tracks(type = "tracks", limit = 13, offset = 0,
time_range = "short_term",authorization = get_spotify_authorization_code(),include_meta_info = FALSE)
```


```{r}
#getting audio features 
year_fav_feature <- get_track_audio_features(year_fav$id, authorization = get_spotify_access_token())
year_fav_feature <- year_fav_feature[, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]

half_year_feature <- get_track_audio_features(half_year_fav$id, authorization = get_spotify_access_token())[, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]

recent_feature <- get_track_audio_features(recent_fav$id, authorization = get_spotify_access_token())[, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]
```


```{r}
#max min normalization 
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

combined_fav <- rbind(year_fav_feature, half_year_feature, recent_feature)
combined_fav_n <- as.data.frame(lapply(combined_fav, normalize)) 
year_fav_mean <- colMeans(combined_fav_n[1:50,])
half_year_fav_n <- colMeans(combined_fav_n[51:75,])
recent_fav_n <- colMeans(combined_fav_n[76:88,])

combined_fav_feature <- data.frame(rbind(year_fav_mean,half_year_fav_n,recent_fav_n))
color = brewer.pal(3,"Paired")
radarchart(combined_fav_feature,axistype=0 ,maxmin=F,
           pcol=color , plwd=2 , plty=1,
           cglcol="grey", cglty=3, axislabcol="grey", cglwd=0.8,vlcex=0.8 )
legend(x=-1.4, y=1.3, legend = c("12 months", "6 months", "3 months"), bty = "n", pch=20 , col=color , text.col = "black",cex=0.8, pt.cex=0.8, y.intersp = 0.8)
#title = "Audio feature preference for the past year"


```

```{r}
playlist1_name <- "chill"
playlist1_uris  <- "4lirpnD9acutQGn1sI8ynJ"
playlist1_features <- get_playlist_audio_features(playlist1_name, playlist1_uris,authorization = get_spotify_access_token())[, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]
playlist1_features <- data.frame(playlist1_features)
rownames(playlist1_features) <- c(paste ("chill", c(1:48)))
```


```{r}
#playlist 2
playlist2_name <- "house&techno"
playlist2_uris  <- "1gw8sDn1VF96t1B7QOfPOF"
playlist2_features <- get_playlist_audio_features(playlist2_name, playlist2_uris,authorization = get_spotify_access_token())[, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]
playlist2_features <- data.frame(playlist2_features)
rownames(playlist2_features) <- c(paste ("H&T", c(1:32)))
```

```{r}
#playlist 3
playlist3_name <- "hip hop"
playlist3_uris <- "0DsnqxDaX9wTarPom1yGSc"
playlist3_features <- get_playlist_audio_features(playlist3_name, playlist3_uris,authorization = get_spotify_access_token())[, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]
playlist3_features <- data.frame(playlist3_features)
rownames(playlist3_features) <- c(paste ("hiphop", c(1:23)))


```

```{r}
#normalize playlists data

combined_full <- as.data.frame(rbind(playlist1_features, playlist2_features, playlist3_features))

combined_full_n <- data.frame(lapply(combined_full,normalize)) %>% `row.names<-`(rownames(combined_full))


chill_mean <- colMeans(combined_full_n[1:49,])

HouseTech_mean <- colMeans(combined_full_n[50:81,])

HipHop_mean <- colMeans(combined_full_n[-23,])

combined_mean <- data.frame(rbind(chill_mean,HouseTech_mean,HipHop_mean ))
```


```{r}
get_track_audio_features(c("0YDSEyBzPsuQzkuc9Bu8iR", "63PjUXm7NNcqm5OCyRMbr5"))[,c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]

```


## Radar plot
```{r}
rownames(combined_mean) <- c("Chill", "House Techno", "Hip Hop")
color_4 <- brewer.pal(4,"Paired")
color4_fill <- add.alpha(color_4,0.3 ) 
radarchart(combined_mean,axistype=0 ,maxmin=F, pcol = color_4, pfcol = color4_fill,plwd=3 , plty=1,
           cglcol="grey", cglty=3, axislabcol="grey", cglwd=0.8,vlcex=0.8 )
legend(x=-1.4, y=1.3, legend = rownames(combined_mean),bty = "n", pch=20,col=color_4,text.col = "black",cex=0.8, pt.cex=0.8)
#title = "My Playlists Audio Features")

```


```{r}
#recently liked music list
liked_song <- get_my_saved_tracks(limit =20 )
recent_liked_feat <-  get_track_audio_features(liked_song$track.id, authorization = get_spotify_access_token())[, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]
recent_liked_feat <- data.frame(recent_liked_feat)
rownames(recent_liked_feat) <- c(paste ("recent_liked", c(1:20)))

recent_n <- as.data.frame(lapply(rbind(recent_liked_feat,combined_full),normalize))

recent_liked_mean <- colMeans(recent_n[1:20,])
recent_combined <- rbind(combined_mean,recent_liked_mean)
rownames(recent_combined) <- c("Chill", "House Techno", "Hip Hop","Recently Liked")

color_4 <- brewer.pal(4,"Paired")
color4_fill <- add.alpha(color_4,0.3 ) 
radarchart(recent_combined, axistype=0 ,maxmin=F, pcol = color_4,plwd=2,   plty=1,cglcol="grey", cglty=3, axislabcol="grey", cglwd=0.8,vlcex=0.8)

legend(x=-1.6, y=1.35, legend = rownames(recent_combined),bty = "n", pch=20,col=color_4,text.col = "black",cex=0.8, pt.cex=0.8,y.intersp = 0.8)





```


```{r}
#weekly discover
playlist_name <- "weekly discovery"
playlist_uris  <- "37i9dQZEVXcUXurUueO6bb"
playlist_disc_features <- get_playlist_audio_features(playlist_name, playlist_uris,authorization = get_spotify_access_token())[1:20, c("danceability", "loudness", "speechiness", "valence","tempo", "acousticness", "energy")]
playlist_disc_features <- data.frame(playlist_disc_features)
rownames(playlist_disc_features) <- c(paste ("discover", c(1:20)))
disc_liked <- rbind(playlist_disc_features, combined_full)
disc_liked_n <- data.frame(lapply(disc_liked,normalize)) %>% `row.names<-`(rownames(disc_liked))

disc_mean <- colMeans(disc_liked_n[1:20,])

disc_combined <- rbind(combined_mean,disc_mean)
rownames(disc_combined) <- c("Chill", "House Techno", "Hip Hop","Discover")

color_4 <- brewer.pal(4,"Paired")
color4_fill <- add.alpha(color_4,0.3 )
radarchart(disc_combined, axistype=0 ,maxmin=F, pcol = color_4, plwd=2 , plty=1,cglcol="grey", cglty=3, axislabcol="grey", cglwd=0.8,vlcex=0.8 )

legend(x= -1.6, y=1.3, legend = rownames(disc_combined),bty = "n", pch=20,col=color_4,text.col = "black",cex=0.8, pt.cex=0.8,y.intersp = 0.8)
#title = "My Playlists Audio Features")

```


## Conclusion: 
#The timeline analysis matches my daily schedule each period: quarantine,summer break,  work 9-5 onsite, work 9-5 remote.The audio feature analysis matches for my playlists matches the genre style, and also I discovered the spotify weekly discover is based on my long-term music preference. 
# I encountered the difficulty on making clear spider graphs, they need to match my color theme and also easy to read. I don't think I did a great good on that. I also had difficulty connecting my specific listening time to the spotify API, that's why I couldn't analyze my prefer audio features through the day (group by morning, afternoon, night, and midnight).

